Zonotoop--a large scale aggregating data warehouse for time-series-based data. [DRAFT]

### 2009-05-05 doc/report/msc-report.tex
usage additions.

@@

@@

@@

\section{Administration}

@@

The user's datasets are defined using YAML--a human friendly data
serialization standard.

>>>>

\begin{verbatim}
   zohmg create project
\end{verbatim}

\noindent Edit the configuration files.

\begin{verbatim}
   zohmg setup
\end{verbatim}

\noindent The above command executes the configuration made and creates the
infrastructure (HBase tables) for the project.

@@

\begin{verbatim}
   zohmg import mappers/somemapper.py path/on/hdfs
\end{verbatim}

@@

\begin{verbatim}
   zohmg serve
\end{verbatim}

\noindent The above serves on default port 8086, with the --port argument it is
possible to change server port.

To extract data, visit the server URL (e.g. http://localhost:8086/) and
give a request and query.

\subsection{Data server}

TODO

URLParser

Client

Data

Transform

@@

\section{Configuration}

@@

The user's datasets are defined using YAML--a human friendly data
serialization standard. The datasets reside in the config directory.

\subsection{Environment}

Certain paths need to be known by OHM in order to function, these are set
in the config/environment.py file.
